Avoiding tipping points in the management of ecological systems: a non-parametric Bayesian approach

### 2013-06-19 inst/doc/nonparametric-bayes.tex
update manuscript examples

>>>>

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{require}\NormalTok{(modeest)}
\NormalTok{posterior.mode <- function(x) \{}
  \KeywordTok{mlv}\NormalTok{(x, }\DataTypeTok{method=}\StringTok{"shorth"}\NormalTok{)$M}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{f <- RickerAllee}
\NormalTok{p <- }\KeywordTok{c}\NormalTok{(}\DecValTok{2}\NormalTok{, }\DecValTok{8}\NormalTok{, }\DecValTok{5}\NormalTok{)}
\NormalTok{K <- }\DecValTok{10}  \CommentTok{# approx, a li'l' less}
\NormalTok{allee <- }\DecValTok{5} \CommentTok{# approx, a li'l' less}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{sigma_g <- }\FloatTok{0.05}
\NormalTok{sigma_m <- }\FloatTok{0.0}
\NormalTok{z_g <- function() }\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{, sigma_g)}
\NormalTok{z_m <- function() }\DecValTok{1}
\NormalTok{x_grid <- }\KeywordTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{1.5} \NormalTok{* K, }\DataTypeTok{length=}\DecValTok{50}\NormalTok{)}
\NormalTok{h_grid <- x_grid}
\NormalTok{profit <- function(x,h) }\KeywordTok{pmin}\NormalTok{(x, h)}
\NormalTok{delta <- }\FloatTok{0.01}
\NormalTok{OptTime <- }\DecValTok{50}  \CommentTok{# stationarity with unstable models is tricky thing}
\NormalTok{reward <- }\DecValTok{0}
\NormalTok{xT <- }\DecValTok{0}
\NormalTok{Xo <-  allee}\FloatTok{+.5}\CommentTok{# observations start from}
\NormalTok{x0 <- K }\CommentTok{# simulation under policy starts from}
\NormalTok{Tobs <- }\DecValTok{40}
\NormalTok{MaxT = }\DecValTok{1000} \CommentTok{# timeout for value iteration convergence}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
  \KeywordTok{set.seed}\NormalTok{(}\DecValTok{1234}\NormalTok{)}
  \CommentTok{#harvest <- sort(rep(seq(0, .5, length=7), 5))}
  \NormalTok{x <- }\KeywordTok{numeric}\NormalTok{(Tobs)}
  \NormalTok{x[}\DecValTok{1}\NormalTok{] <- Xo}
  \NormalTok{nz <- }\DecValTok{1}
  \NormalTok{for(t in }\DecValTok{1}\NormalTok{:(Tobs}\DecValTok{-1}\NormalTok{))}
    \NormalTok{x[t}\DecValTok{+1}\NormalTok{] = }\KeywordTok{z_g}\NormalTok{() * }\KeywordTok{f}\NormalTok{(x[t], }\DataTypeTok{h=}\DecValTok{0}\NormalTok{, }\DataTypeTok{p=}\NormalTok{p)}
  \NormalTok{obs <- }\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{x =} \KeywordTok{c}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nz), }
                          \KeywordTok{pmax}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,Tobs}\DecValTok{-1}\NormalTok{), x[}\DecValTok{1}\NormalTok{:(Tobs}\DecValTok{-1}\NormalTok{)])), }
                    \DataTypeTok{y =} \KeywordTok{c}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nz), }
                          \NormalTok{x[}\DecValTok{2}\NormalTok{:Tobs]))}
\NormalTok{raw_plot <- }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{time =} \DecValTok{1}\NormalTok{:Tobs, }\DataTypeTok{x=}\NormalTok{x), }\KeywordTok{aes}\NormalTok{(time,x)) + }\KeywordTok{geom_line}\NormalTok{()}
\NormalTok{raw_plot}
\end{Highlighting}
\end{Shaded}

\begin{figure}[htbp]
\centering
\includegraphics{figure/obs.pdf}
\caption{plot of chunk obs}
\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{12345}\NormalTok{)}
\NormalTok{estf <- function(p)\{ }
    \NormalTok{mu <- }\KeywordTok{f}\NormalTok{(obs$x,}\DecValTok{0}\NormalTok{,p)}
    \NormalTok{-}\KeywordTok{sum}\NormalTok{(}\KeywordTok{dlnorm}\NormalTok{(obs$y, }\KeywordTok{log}\NormalTok{(mu), p[}\DecValTok{4}\NormalTok{]), }\DataTypeTok{log=}\OtherTok{TRUE}\NormalTok{)}
\NormalTok{\}}
\NormalTok{par <- }\KeywordTok{c}\NormalTok{(p[}\DecValTok{1}\NormalTok{]*}\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{0}\NormalTok{,.}\DecValTok{1}\NormalTok{), }
         \NormalTok{p[}\DecValTok{2}\NormalTok{]*}\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{0}\NormalTok{,.}\DecValTok{1}\NormalTok{), }
         \NormalTok{p[}\DecValTok{3}\NormalTok{]*}\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{0}\NormalTok{, .}\DecValTok{1}\NormalTok{), }
         \NormalTok{sigma_g * }\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{0}\NormalTok{,.}\DecValTok{1}\NormalTok{))}
\NormalTok{o <- }\KeywordTok{optim}\NormalTok{(par, estf, }\DataTypeTok{method=}\StringTok{"L"}\NormalTok{, }\DataTypeTok{lower=}\KeywordTok{c}\NormalTok{(}\FloatTok{1e-5}\NormalTok{,}\FloatTok{1e-5}\NormalTok{,}\FloatTok{1e-5}\NormalTok{,}\FloatTok{1e-5}\NormalTok{))}
\NormalTok{f_alt <- f}
\NormalTok{p_alt <- }\KeywordTok{c}\NormalTok{(}\KeywordTok{as.numeric}\NormalTok{(o$par[}\DecValTok{1}\NormalTok{]), }\KeywordTok{as.numeric}\NormalTok{(o$par[}\DecValTok{2}\NormalTok{]), }\KeywordTok{as.numeric}\NormalTok{(o$par[}\DecValTok{3}\NormalTok{]))}
\NormalTok{sigma_g_alt <- }\KeywordTok{as.numeric}\NormalTok{(o$par[}\DecValTok{4}\NormalTok{])}

\NormalTok{est <- }\KeywordTok{list}\NormalTok{(}\DataTypeTok{f =} \NormalTok{f_alt, }\DataTypeTok{p =} \NormalTok{p_alt, }\DataTypeTok{sigma_g =} \NormalTok{sigma_g_alt, }\DataTypeTok{mloglik=}\NormalTok{o$value)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{true_means <- }\KeywordTok{sapply}\NormalTok{(x_grid, f, }\DecValTok{0}\NormalTok{, p)}
\NormalTok{est_means <- }\KeywordTok{sapply}\NormalTok{(x_grid, est$f, }\DecValTok{0}\NormalTok{, est$p)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#inv gamma has mean b / (a - 1) (assuming a>1) and variance b ^ 2 / ((a - 2) * (a - 1) ^ 2) (assuming a>2)}
\NormalTok{s2.p <- }\KeywordTok{c}\NormalTok{(}\DecValTok{5}\NormalTok{,}\DecValTok{5}\NormalTok{)  }
\NormalTok{d.p = }\KeywordTok{c}\NormalTok{(}\DecValTok{10}\NormalTok{, }\DecValTok{1}\NormalTok{/}\FloatTok{0.1}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{gp <- }\KeywordTok{gp_mcmc}\NormalTok{(obs$x, }\DataTypeTok{y=}\NormalTok{obs$y, }\DataTypeTok{n=}\FloatTok{1e5}\NormalTok{, }\DataTypeTok{s2.p =} \NormalTok{s2.p, }\DataTypeTok{d.p =} \NormalTok{d.p)}
\NormalTok{gp_dat <- }\KeywordTok{gp_predict}\NormalTok{(gp, x_grid, }\DataTypeTok{burnin=}\FloatTok{1e4}\NormalTok{, }\DataTypeTok{thin=}\DecValTok{300}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{gp_assessment_plots <- }\KeywordTok{summary_gp_mcmc}\NormalTok{(gp, }\DataTypeTok{burnin=}\FloatTok{1e4}\NormalTok{, }\DataTypeTok{thin=}\DecValTok{300}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Summarize the GP model}
\NormalTok{tgp_dat <- }
    \KeywordTok{data.frame}\NormalTok{(  }\DataTypeTok{x =} \NormalTok{x_grid, }
                 \DataTypeTok{y =} \NormalTok{gp_dat$E_Ef, }
                 \DataTypeTok{ymin =} \NormalTok{gp_dat$E_Ef - }\DecValTok{2} \NormalTok{* }\KeywordTok{sqrt}\NormalTok{(gp_dat$E_Vf), }
                 \DataTypeTok{ymax =} \NormalTok{gp_dat$E_Ef + }\DecValTok{2} \NormalTok{* }\KeywordTok{sqrt}\NormalTok{(gp_dat$E_Vf) )}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{y <- x }
\NormalTok{N <- }\KeywordTok{length}\NormalTok{(x);}
\NormalTok{jags.data <- }\KeywordTok{list}\NormalTok{(}\StringTok{"N"}\NormalTok{,}\StringTok{"y"}\NormalTok{)}
\NormalTok{n.chains <- }\DecValTok{6}
\NormalTok{n.iter <- }\FloatTok{1e6}
\NormalTok{n.burnin <- }\KeywordTok{floor}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
\NormalTok{n.thin <- }\KeywordTok{max}\NormalTok{(}\DecValTok{1}\NormalTok{, }\KeywordTok{floor}\NormalTok{(n.chains * (n.iter - n.burnin)/}\DecValTok{1000}\NormalTok{))}
\NormalTok{n.update <- }\DecValTok{10}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{stdQ_prior_p <- }\KeywordTok{c}\NormalTok{(}\FloatTok{1e-6}\NormalTok{, }\DecValTok{100}\NormalTok{)}
\NormalTok{stdR_prior_p <- }\KeywordTok{c}\NormalTok{(}\FloatTok{1e-6}\NormalTok{, .}\DecValTok{1}\NormalTok{)}
\NormalTok{stdQ_prior  <- function(x) }\KeywordTok{dunif}\NormalTok{(x, stdQ_prior_p[}\DecValTok{1}\NormalTok{], stdQ_prior_p[}\DecValTok{2}\NormalTok{])}
\NormalTok{stdR_prior  <- function(x) }\KeywordTok{dunif}\NormalTok{(x, stdR_prior_p[}\DecValTok{1}\NormalTok{], stdR_prior_p[}\DecValTok{2}\NormalTok{])}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{K_prior_p <- }\KeywordTok{c}\NormalTok{(}\FloatTok{0.01}\NormalTok{, }\FloatTok{20.0}\NormalTok{)}
\NormalTok{r0_prior_p <- }\KeywordTok{c}\NormalTok{(}\FloatTok{0.01}\NormalTok{, }\FloatTok{6.0}\NormalTok{)}
\NormalTok{theta_prior_p <- }\KeywordTok{c}\NormalTok{(}\FloatTok{0.01}\NormalTok{, }\FloatTok{20.0}\NormalTok{)}

\NormalTok{bugs.model <- }
\KeywordTok{paste}\NormalTok{(}\KeywordTok{sprintf}\NormalTok{(}
\StringTok{"model\{}
\StringTok{  K     ~ dunif(%s, %s)}
\StringTok{  r0    ~ dunif(%s, %s)}
\StringTok{  theta ~ dunif(%s, %s)}
\StringTok{  stdQ ~ dunif(%s, %s)"}\NormalTok{, }
  \NormalTok{K_prior_p[}\DecValTok{1}\NormalTok{], K_prior_p[}\DecValTok{2}\NormalTok{],}
  \NormalTok{r0_prior_p[}\DecValTok{1}\NormalTok{], r0_prior_p[}\DecValTok{2}\NormalTok{],}
  \NormalTok{theta_prior_p[}\DecValTok{1}\NormalTok{], theta_prior_p[}\DecValTok{2}\NormalTok{],}
  \NormalTok{stdQ_prior_p[}\DecValTok{1}\NormalTok{], stdQ_prior_p[}\DecValTok{2}\NormalTok{]),}

  \StringTok{"}
\StringTok{  iQ <- 1 / (stdQ * stdQ);}
\StringTok{  y[1] ~ dunif(0, 10)}
\StringTok{  for(t in 1:(N-1))\{}
\StringTok{    mu[t] <- log(y[t]) + r0 * (1 - y[t]/K)* (y[t] - theta) / K }
\StringTok{    y[t+1] ~ dlnorm(mu[t], iQ) }
\StringTok{  \}}
\StringTok{\}"}\NormalTok{)}
\KeywordTok{writeLines}\NormalTok{(bugs.model, }\StringTok{"allen_process.bugs"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{K_prior     <- function(x) }\KeywordTok{dunif}\NormalTok{(x, K_prior_p[}\DecValTok{1}\NormalTok{], K_prior_p[}\DecValTok{2}\NormalTok{])}
\NormalTok{r0_prior <- function(x) }\KeywordTok{dunif}\NormalTok{(x, r0_prior_p[}\DecValTok{1}\NormalTok{], r0_prior_p[}\DecValTok{2}\NormalTok{])}
\NormalTok{theta_prior <- function(x) }\KeywordTok{dunif}\NormalTok{(x, theta_prior_p[}\DecValTok{1}\NormalTok{], theta_prior_p[}\DecValTok{2}\NormalTok{])}
\NormalTok{par_priors  <- }\KeywordTok{list}\NormalTok{(}\DataTypeTok{K =} \NormalTok{K_prior, }\DataTypeTok{deviance =} \NormalTok{function(x) }\DecValTok{0} \NormalTok{* x, }
                    \DataTypeTok{r0 =} \NormalTok{r0_prior, }\DataTypeTok{theta =} \NormalTok{theta_prior,}
                    \DataTypeTok{stdQ =} \NormalTok{stdQ_prior)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{jags.params=}\KeywordTok{c}\NormalTok{(}\StringTok{"K"}\NormalTok{,}\StringTok{"r0"}\NormalTok{,}\StringTok{"theta"}\NormalTok{,}\StringTok{"stdQ"}\NormalTok{) }\CommentTok{# be sensible about the order here}
\NormalTok{jags.inits <- function()\{}
  \KeywordTok{list}\NormalTok{(}\StringTok{"K"}\NormalTok{= }\DecValTok{10} \NormalTok{* }\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{0}\NormalTok{, }\FloatTok{0.1}\NormalTok{),}
       \StringTok{"r0"}\NormalTok{= }\DecValTok{1} \NormalTok{* }\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{0}\NormalTok{, }\FloatTok{0.1}\NormalTok{) ,}
       \StringTok{"theta"}\NormalTok{=   }\DecValTok{5} \NormalTok{* }\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{0}\NormalTok{, }\FloatTok{0.1}\NormalTok{) , }
       \StringTok{"stdQ"}\NormalTok{= }\KeywordTok{abs}\NormalTok{( }\FloatTok{0.1} \NormalTok{* }\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{0}\NormalTok{, }\FloatTok{0.1}\NormalTok{)),}
       \DataTypeTok{.RNG.name=}\StringTok{"base::Wichmann-Hill"}\NormalTok{, }\DataTypeTok{.RNG.seed=}\DecValTok{123}\NormalTok{)}
\NormalTok{\}}

\KeywordTok{set.seed}\NormalTok{(}\DecValTok{1234}\NormalTok{)}
\CommentTok{# parallel refuses to take variables as arguments (e.g. n.iter = 1e5 works, but n.iter = n doesn't)}
\NormalTok{allen_jags <- }\KeywordTok{do.call}\NormalTok{(jags.parallel, }\KeywordTok{list}\NormalTok{(}\DataTypeTok{data=}\NormalTok{jags.data, }\DataTypeTok{inits=}\NormalTok{jags.inits, }
                                      \NormalTok{jags.params, }\DataTypeTok{n.chains=}\NormalTok{n.chains, }
                                      \DataTypeTok{n.iter=}\NormalTok{n.iter, }\DataTypeTok{n.thin=}\NormalTok{n.thin, }
                                      \DataTypeTok{n.burnin=}\NormalTok{n.burnin, }
                                      \DataTypeTok{model.file=}\StringTok{"allen_process.bugs"}\NormalTok{))}

\CommentTok{# Run again iteratively if we haven't met the Gelman-Rubin convergence criterion}
\KeywordTok{recompile}\NormalTok{(allen_jags) }\CommentTok{# required for parallel}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
   Graph Size: 328

Initializing model

Compiling model graph
   Resolving undeclared variables
   Allocating nodes
   Graph Size: 328

Initializing model

Compiling model graph
   Resolving undeclared variables
   Allocating nodes
   Graph Size: 328

Initializing model

Compiling model graph
   Resolving undeclared variables
   Allocating nodes
   Graph Size: 328

Initializing model

Compiling model graph
   Resolving undeclared variables
   Allocating nodes
   Graph Size: 328

Initializing model

Compiling model graph
   Resolving undeclared variables
   Allocating nodes
   Graph Size: 328

Initializing model
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{allen_jags <- }\KeywordTok{do.call}\NormalTok{(autojags, }
                                            \KeywordTok{list}\NormalTok{(}\DataTypeTok{object=}\NormalTok{allen_jags, }\DataTypeTok{n.update=}\NormalTok{n.update, }
                           \DataTypeTok{n.iter=}\NormalTok{n.iter, }\DataTypeTok{n.thin =} \NormalTok{n.thin))}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{tmp <- }\KeywordTok{lapply}\NormalTok{(}\KeywordTok{as.mcmc}\NormalTok{(allen_jags), as.matrix) }\CommentTok{# strip classes the hard way...}
\NormalTok{allen_posteriors <- }\KeywordTok{melt}\NormalTok{(tmp, }\DataTypeTok{id =} \KeywordTok{colnames}\NormalTok{(tmp[[}\DecValTok{1}\NormalTok{]])) }
\KeywordTok{names}\NormalTok{(allen_posteriors) = }\KeywordTok{c}\NormalTok{(}\StringTok{"index"}\NormalTok{, }\StringTok{"variable"}\NormalTok{, }\StringTok{"value"}\NormalTok{, }\StringTok{"chain"}\NormalTok{)}
\NormalTok{plot_allen_traces <- }\KeywordTok{ggplot}\NormalTok{(allen_posteriors) + }\KeywordTok{geom_line}\NormalTok{(}\KeywordTok{aes}\NormalTok{(index, value)) + }
  \KeywordTok{facet_wrap}\NormalTok{(~ variable, }\DataTypeTok{scale=}\StringTok{"free"}\NormalTok{, }\DataTypeTok{ncol=}\DecValTok{1}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{allen_priors <- }\KeywordTok{ddply}\NormalTok{(allen_posteriors, }\StringTok{"variable"}\NormalTok{, function(dd)\{}
    \NormalTok{grid <- }\KeywordTok{seq}\NormalTok{(}\KeywordTok{min}\NormalTok{(dd$value), }\KeywordTok{max}\NormalTok{(dd$value), }\DataTypeTok{length =} \DecValTok{100}\NormalTok{) }
    \KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{value =} \NormalTok{grid, }\DataTypeTok{density =} \NormalTok{par_priors[[dd$variable[}\DecValTok{1}\NormalTok{]]](grid))}
\NormalTok{\})}
\NormalTok{plot_allen_posteriors <- }\KeywordTok{ggplot}\NormalTok{(allen_posteriors, }\KeywordTok{aes}\NormalTok{(value)) + }
  \KeywordTok{stat_density}\NormalTok{(}\DataTypeTok{geom=}\StringTok{"path"}\NormalTok{, }\DataTypeTok{position=}\StringTok{"identity"}\NormalTok{, }\DataTypeTok{alpha=}\FloatTok{0.7}\NormalTok{) +}
  \KeywordTok{geom_line}\NormalTok{(}\DataTypeTok{data=}\NormalTok{allen_priors, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{value, }\DataTypeTok{y=}\NormalTok{density), }\DataTypeTok{col=}\StringTok{"red"}\NormalTok{) + }
  \KeywordTok{facet_wrap}\NormalTok{(~ variable, }\DataTypeTok{scale=}\StringTok{"free"}\NormalTok{, }\DataTypeTok{ncol=}\DecValTok{3}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{A <- allen_posteriors}
\NormalTok{A$index <- A$index + A$chain * }\KeywordTok{max}\NormalTok{(A$index) }\CommentTok{# Combine samples across chains by renumbering index }
\NormalTok{pardist <- }\KeywordTok{acast}\NormalTok{(A, index ~ variable)}
\NormalTok{bayes_coef <- }\KeywordTok{apply}\NormalTok{(pardist,}\DecValTok{2}\NormalTok{, posterior.mode) }
\NormalTok{bayes_pars <- }\KeywordTok{unname}\NormalTok{(}\KeywordTok{c}\NormalTok{(bayes_coef[}\StringTok{"r0"}\NormalTok{], bayes_coef[}\StringTok{"K"}\NormalTok{], bayes_coef[}\StringTok{"theta"}\NormalTok{])) }\CommentTok{# parameters formatted for f}
\NormalTok{allen_f <- function(x,h,p) }\KeywordTok{unname}\NormalTok{(}\KeywordTok{RickerAllee}\NormalTok{(x,h, }\KeywordTok{unname}\NormalTok{(p[}\KeywordTok{c}\NormalTok{(}\StringTok{"r0"}\NormalTok{, }\StringTok{"K"}\NormalTok{, }\StringTok{"theta"}\NormalTok{)])))}
\NormalTok{allen_means <- }\KeywordTok{sapply}\NormalTok{(x_grid, f, }\DecValTok{0}\NormalTok{, bayes_pars)}
\NormalTok{bayes_pars}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
[1] 0.5003 7.7115 4.6039
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{head}\NormalTok{(pardist)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
        K deviance     r0    stdQ theta
170 7.898    34.41 0.6668 0.05566 3.956
171 7.745    32.76 0.7554 0.05137 4.668
172 7.577    31.66 1.0705 0.04562 4.073
173 7.859    31.26 1.5647 0.04238 5.087
174 7.821    30.67 1.7348 0.04662 5.230
175 8.003    34.90 1.4495 0.05005 5.444
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{K_prior_p <- }\KeywordTok{c}\NormalTok{(}\FloatTok{0.01}\NormalTok{, }\FloatTok{40.0}\NormalTok{)}
\NormalTok{r0_prior_p <- }\KeywordTok{c}\NormalTok{(}\FloatTok{0.01}\NormalTok{, }\FloatTok{20.0}\NormalTok{)}
\NormalTok{bugs.model <- }
\KeywordTok{paste}\NormalTok{(}\KeywordTok{sprintf}\NormalTok{(}
\StringTok{"model\{}
\StringTok{  K    ~ dunif(%s, %s)}
\StringTok{  r0    ~ dunif(%s, %s)}
\StringTok{  stdQ ~ dunif(%s, %s)"}\NormalTok{, }
  \NormalTok{K_prior_p[}\DecValTok{1}\NormalTok{], K_prior_p[}\DecValTok{2}\NormalTok{],}
  \NormalTok{r0_prior_p[}\DecValTok{1}\NormalTok{], r0_prior_p[}\DecValTok{2}\NormalTok{],}
  \NormalTok{stdQ_prior_p[}\DecValTok{1}\NormalTok{], stdQ_prior_p[}\DecValTok{2}\NormalTok{]),}
  \StringTok{"}
\StringTok{  iQ <- 1 / (stdQ * stdQ);}
\StringTok{  y[1] ~ dunif(0, 10)}
\StringTok{  for(t in 1:(N-1))\{}
\StringTok{    mu[t] <- log(y[t]) + r0 * (1 - y[t]/K) }
\StringTok{    y[t+1] ~ dlnorm(mu[t], iQ) }
\StringTok{  \}}
\StringTok{\}"}\NormalTok{)}
\KeywordTok{writeLines}\NormalTok{(bugs.model, }\StringTok{"ricker_process.bugs"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{K_prior     <- function(x) }\KeywordTok{dunif}\NormalTok{(x, K_prior_p[}\DecValTok{1}\NormalTok{], K_prior_p[}\DecValTok{2}\NormalTok{])}
\NormalTok{r0_prior <- function(x) }\KeywordTok{dunif}\NormalTok{(x, r0_prior_p[}\DecValTok{1}\NormalTok{], r0_prior_p[}\DecValTok{2}\NormalTok{])}
\NormalTok{par_priors <- }\KeywordTok{list}\NormalTok{(}\DataTypeTok{K =} \NormalTok{K_prior, }\DataTypeTok{deviance =} \NormalTok{function(x) }\DecValTok{0} \NormalTok{* x, }
                   \DataTypeTok{r0 =} \NormalTok{r0_prior, }\DataTypeTok{stdQ =} \NormalTok{stdQ_prior)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{jags.params=}\KeywordTok{c}\NormalTok{(}\StringTok{"K"}\NormalTok{,}\StringTok{"r0"}\NormalTok{, }\StringTok{"stdQ"}\NormalTok{)}
\NormalTok{jags.inits <- function()\{}
  \KeywordTok{list}\NormalTok{(}\StringTok{"K"}\NormalTok{= }\DecValTok{10} \NormalTok{* }\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{0}\NormalTok{,.}\DecValTok{5}\NormalTok{),}
       \StringTok{"r0"}\NormalTok{= }\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{0}\NormalTok{,.}\DecValTok{5}\NormalTok{),}
       \StringTok{"stdQ"}\NormalTok{=}\KeywordTok{sqrt}\NormalTok{(}\FloatTok{0.05}\NormalTok{) * }\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{0}\NormalTok{,.}\DecValTok{5}\NormalTok{),}
       \DataTypeTok{.RNG.name=}\StringTok{"base::Wichmann-Hill"}\NormalTok{, }\DataTypeTok{.RNG.seed=}\DecValTok{123}\NormalTok{)}
\NormalTok{\}}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{12345}\NormalTok{) }
\NormalTok{ricker_jags <- }\KeywordTok{do.call}\NormalTok{(jags.parallel, }
                       \KeywordTok{list}\NormalTok{(}\DataTypeTok{data=}\NormalTok{jags.data, }\DataTypeTok{inits=}\NormalTok{jags.inits, }
                            \NormalTok{jags.params, }\DataTypeTok{n.chains=}\NormalTok{n.chains, }
                            \DataTypeTok{n.iter=}\NormalTok{n.iter, }\DataTypeTok{n.thin=}\NormalTok{n.thin, }\DataTypeTok{n.burnin=}\NormalTok{n.burnin,}
                            \DataTypeTok{model.file=}\StringTok{"ricker_process.bugs"}\NormalTok{))}
\KeywordTok{recompile}\NormalTok{(ricker_jags)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
   Graph Size: 249

Initializing model

Compiling model graph
   Resolving undeclared variables
   Allocating nodes
   Graph Size: 249

Initializing model

Compiling model graph
   Resolving undeclared variables
   Allocating nodes
   Graph Size: 249

Initializing model

Compiling model graph
   Resolving undeclared variables
   Allocating nodes
   Graph Size: 249

Initializing model

Compiling model graph
   Resolving undeclared variables
   Allocating nodes
   Graph Size: 249

Initializing model

Compiling model graph
   Resolving undeclared variables
   Allocating nodes
   Graph Size: 249

Initializing model
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{ricker_jags <- }\KeywordTok{do.call}\NormalTok{(autojags, }
                       \KeywordTok{list}\NormalTok{(}\DataTypeTok{object=}\NormalTok{ricker_jags, }\DataTypeTok{n.update=}\NormalTok{n.update, }
                                                        \DataTypeTok{n.iter=}\NormalTok{n.iter, }\DataTypeTok{n.thin =} \NormalTok{n.thin, }
                                                        \DataTypeTok{progress.bar=}\StringTok{"none"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{tmp <- }\KeywordTok{lapply}\NormalTok{(}\KeywordTok{as.mcmc}\NormalTok{(ricker_jags), as.matrix) }\CommentTok{# strip classes the hard way...}
\NormalTok{ricker_posteriors <- }\KeywordTok{melt}\NormalTok{(tmp, }\DataTypeTok{id =} \KeywordTok{colnames}\NormalTok{(tmp[[}\DecValTok{1}\NormalTok{]])) }
\KeywordTok{names}\NormalTok{(ricker_posteriors) = }\KeywordTok{c}\NormalTok{(}\StringTok{"index"}\NormalTok{, }\StringTok{"variable"}\NormalTok{, }\StringTok{"value"}\NormalTok{, }\StringTok{"chain"}\NormalTok{)}
\NormalTok{plot_ricker_traces <- }\KeywordTok{ggplot}\NormalTok{(ricker_posteriors) + }\KeywordTok{geom_line}\NormalTok{(}\KeywordTok{aes}\NormalTok{(index, value)) + }
  \KeywordTok{facet_wrap}\NormalTok{(~ variable, }\DataTypeTok{scale=}\StringTok{"free"}\NormalTok{, }\DataTypeTok{ncol=}\DecValTok{1}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{ricker_priors <- }\KeywordTok{ddply}\NormalTok{(ricker_posteriors, }\StringTok{"variable"}\NormalTok{, function(dd)\{}
    \NormalTok{grid <- }\KeywordTok{seq}\NormalTok{(}\KeywordTok{min}\NormalTok{(dd$value), }\KeywordTok{max}\NormalTok{(dd$value), }\DataTypeTok{length =} \DecValTok{100}\NormalTok{) }
    \KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{value =} \NormalTok{grid, }\DataTypeTok{density =} \NormalTok{par_priors[[dd$variable[}\DecValTok{1}\NormalTok{]]](grid))}
\NormalTok{\})}
\CommentTok{# plot posterior distributions}
\NormalTok{plot_ricker_posteriors <- }\KeywordTok{ggplot}\NormalTok{(ricker_posteriors, }\KeywordTok{aes}\NormalTok{(value)) + }
  \KeywordTok{stat_density}\NormalTok{(}\DataTypeTok{geom=}\StringTok{"path"}\NormalTok{, }\DataTypeTok{position=}\StringTok{"identity"}\NormalTok{, }\DataTypeTok{alpha=}\FloatTok{0.7}\NormalTok{) +}
  \KeywordTok{geom_line}\NormalTok{(}\DataTypeTok{data=}\NormalTok{ricker_priors, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{value, }\DataTypeTok{y=}\NormalTok{density), }\DataTypeTok{col=}\StringTok{"red"}\NormalTok{) + }
  \KeywordTok{facet_wrap}\NormalTok{(~ variable, }\DataTypeTok{scale=}\StringTok{"free"}\NormalTok{, }\DataTypeTok{ncol=}\DecValTok{2}\NormalTok{)}
\end{Highlighting}
\end{Shaded}
